\tit

### 2021-02-28 paper.tex
"(which are essentially \emph{proof-relevant} recognizers)"

Of the previous work involving language derivatives, none appear to have based their formal specification and proofs on the essential, non-inductive, nearly-trivial definition in terms of functions of lists from \secref{Decomposing Languages}.
\citet{Abel2016} mentioned this definition informally as motivation for the more complex, coinductively defined operations on tries.
\citet{Brzozowski64} also made clear mention of the underlying meaning on sets of strings in his original work on regular expression derivatives.
Moreover, none of these previous investigations appear to have addressed proof isomorphism (distinguishing multiple parsings/explanations), and correspondingly all use transformations based the less precise laws originally discovered by \citet{Brzozowski64}.
Those laws were based on the assumption that union (``addition'' in both language semirings of \secref{Predicate Algebra}) is idempotent, which is not true for type-level language predicates related by proof isomorphism (rather than mere logical equivalence).
The lack of idempotence is crucial for going beyond recognizers to parsers, in which we might want to extract more than one proof (parsing).
The difference is mainly visible in the \AF ν and \AF δ lemmas for {\AB P ⋆ \AB Q} and {\AB P ☆} in \figref{nu-delta-lemmas}.

>>>>

Of the previous work involving language derivatives, none appear to have based their formal specification and proofs on the essential, non-inductive, nearly-trivial definition in terms of functions of lists from \secref{Decomposing Languages}.
\citet{Abel2016} mentioned this definition informally as motivation for the more complex, coinductively defined operations on tries.
\citet{Brzozowski64} also made clear mention of the underlying meaning on sets of strings in his original work on regular expression derivatives.
Moreover, none of these previous investigations appear to have addressed proof isomorphism (distinguishing multiple parsings/explanations), and correspondingly all use transformations based the less precise laws originally discovered by \citet{Brzozowski64}.
Those laws were based on the assumption that union (``addition'' in both language semirings of \secref{Predicate Algebra}) is idempotent, which is not true for type-level language predicates related by proof isomorphism (rather than mere logical equivalence).
The lack of idempotence is crucial for going beyond recognizers to parsers (which are essentially \emph{proof-relevant} recognizers), in which we might want to extract more than one proof (parsing).
The difference is mainly visible in the \AF ν and \AF δ lemmas for {\AB P ⋆ \AB Q} and {\AB P ☆} in \figref{nu-delta-lemmas}.
